%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% (v1.0, May 16 2024) written by Genki Ogaki (rockstarogk@gmail.com). Compiles with XeLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}
\usepackage{verbatim}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand{\mysection}[1]{\textbf{\large #1}}

\newcommand*{\experienceentry}[2]{
    \begin{tabularx}{\textwidth}{X r}
        \raisebox{-0.75ex}{\subsection{\textbf{#1}}} & \raisebox{-0.75ex}{\itshape #2}
    \end{tabularx}
}
\newcommand*{\subexperienceentry}[2]{
    \begin{tabularx}{\textwidth}{LR}
        \textbf{#1} & {\itshape #2}
    \end{tabularx}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

% preamble
\firstname{Meet}
\familyname{Patel}
\address{Bangalore, India}{}

% document
\begin{document}
\maketitle
\vspace{-7.0mm}
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \emaillink{patel.meet@gmail.com} & \mobilephonesymbol\enspace (+91) 95375-99710 & \faLinkedin\enspace \href{https://www.linkedin.com/in/patelmeet953/}{linkedin.com/in/patelmeet953}
\end{tabularx}
\vspace{-2.0mm}

\section{SUMMARY}
Highly motivated and results-oriented Software Engineer (M.Tech Data Science) with 6+ years' experience building critical e-commerce functionalities at Flipkart. Expertise in microservices, big data distributed technologies, software design and product development. Proven ability to leverage data science and cloud technologies to drive growth and user experience.
\vspace{2.0mm}

% left column
\begin{minipage}[t]{0.62\textwidth}
\section{EXPERIENCE}
\experienceentry{Flipkart}{Bangalore, India}

\subexperienceentry{SDE-3}{Jul 2023 - Present}
Team Lead and Scrum Master
\begin{itemize}
    \item Scrum Master for Brand Regulation and Selection Insights team of 8 members
    \item Streamlined on-call and seller issue process, reducing maintenance effort. Overall KTLO reduced by 60\%. Led optimizations in brand regulation platform improving scale by 100\% and latency by 40\%.
    \item Leading the Brand Hub project: a brand owner portal for seller and product management with violation reporting functionalities.
    \item Leading New selection discovery project: collaborate with data science to predict new product’s potential and work with search team to provide them boost in discovery funnels.
\end{itemize}
\vspace{1.0mm}
\textbf {Skills}: Communication, Leadership, Problem-Solving, Agile Methodology (SDLC), Microservices Architecture, Big Data Engineering
\vspace{3.0mm}

\subexperienceentry{SDE-2}{Jan 2020 - Jun 2023}
Lead Backend Developer
\begin{itemize}
    \item Expanded seller recommendations (high-demand sold out, best selling, stock recommendations, search trends etc), revamped the system for improved coverage and cold-start. Scalable data pipeline using Spark and Kafka.
    \item Led the "better-priced similar product" system. Work with data science team to identify cost-effective alternatives for high-demand products, ultimately recommending them to budget-conscious customers.
\end{itemize}
\vspace{1.0mm}
\textbf {Technologies}: Java, Dropwizard, Spark, Scala, Elasticsearch, MySQL, Kafka, Pulsar
\vspace{3.0mm}

\subexperienceentry{SDE-1}{Jul 2018 - Dec 2019}
Backend Developer
\begin{itemize}
    \item Developed a competitive selection benchmarking platform.
    \item Selection gaps identification and fulfilment system.
\end{itemize}
\vspace{1.0mm}
\textbf {Technologies}: Hive, Python, Airflow, Java, MySQL, Kafka
\vspace{3.0mm}

\subexperienceentry{Intern}{Jan 2018 - Jun 2018}
Search query analysis - improve clustering of similar intent queries and Identifying low-performing queries. \\
\textbf {Technologies}: Hive, HDFS, MapReduce, Python, MySQL
\vspace{3.0mm}


\end{minipage}
\hfill
% right column
\begin{minipage}[t]{0.35\textwidth}

\section{EDUCATION}
\educationentry{M.Tech, IT\\Data Science specialization}{IIIT - Bangalore}{Bangalore, India}
GPA: 3.9/4.0
\par
\vspace{3.0mm}
\educationentry{B.Tech, Computer Science}{DDIT}{Nadiad, India}
GPA: 7.9/10.0

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
Back End & Java, Python, Scala \\
Databases & MySQL, ElasticSearch \\
DevOps & Docker, Kubernates, Git \\
BigData & Spark, Hadoop \\
Misc. & Kafka, Airflow, GCP \\
OS & macOS, Linux \\
\end{tabularx}


\section{ACHIEVEMENTS}
\scoreentry{Instant Karma - Flipkart}{Instant Karma award for "Better priced similar product" work}
\scoreentry{Dean Scholarship Award - IIITB}{Award at Convocation for being top performer}
\scoreentry{Gate Exam}{AIR: 741}


\section{LANGUAGES}
\begin{itemize}
    \item English (Advanced)
    \item Hindi (Advanced)
    \item Gujarati (Native)
\end{itemize}


\end{minipage}

\end{document}
